Submission HW1

### 2022-08-29 hw1-1/submission.Rmd
residual commits

---
title: "Submission HW1"
output:
  html_document:
    df_print: paged
---

# Submission for HW1 \| ISYE 6501 \| Fall 22

@@

-   Abhinav Arun \|

-   Anshit Verma \|

@@

**Describe a situation or problem from your job, everyday life, current events, etc., for which a classification model would be appropriate. List some (up to 5) predictors that you might use.**

@@

**The files credit_card_data.txt (without headers) and credit_card_data-headers.txt (with headers) contain a dataset with 654 data points, 6 continuous and 4 binary predictor variables. It has anonymized credit card applications with a binary response variable (last column) indicating if the application was positive or negative.**

@@

@@

-   R1: A8,A9,A10,A11

@@

## Question 2.2 (part 1)

**Using the support vector machine function ksvm contained in the R package kernlab, find a good classifier for this data. Show the equation of your classifier, and how well it classifies the data points in the full data set. (Don't worry about test/validation data yet; we'll cover that topic soon.)**

@@

@@

@@

>>>>

---
title: "Submission HW1"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# ISYE 6501 \| Fall 22

@@

-   Abhinav Arun \| [aarun60\@gatech.edu](mailto:aarun60gatech.edu){.email}

-   Anshit Verma \| [averma373\@gatech.edu](mailto:averma373@gatech.edu){.email}

[**\*Analysis Notes are marked with Red header: #Analysis**]{style="color:red"}

@@

@@

@@

[**#Analysis:**]{style="color:red"}

@@

-   R1: A8,A9,A10,A11 (We expect these to show up with high weights in SVM eqn.)

@@

## Question 2.2 (part 1: kSVM with Linear kernel)

@@

[**#Analysis:**]{style="color:red"}
**There are 190 support vectors, or roughly 30% of the total data points.

@@

[**#Analysis:**]{style="color:red"}
**With increasing C, we weight the cost function more towards misclassification (realtive to margin). Therefore intuitively incereasing C, should increase Accuracy albeit at the cost of margin. And in the above data points too, similar effect is apparent**

@@

### v1: Equation of SVM
$W = \sum_i(\alpha Y_i X_{support\_vector_i})$$
